An Empirical Study of Work Fragmentation in Software Evolution Tasks

### 2015-08-03 paper_v2.tex
Nuevos capitulos añadidos. Borrador
Faltan los graficos, discusion, introduccion y limitaciones

\subsection{Local Analysis}
Having presented the global effect of the interruptions over the user productivity, we now focus on the local activity before and after interruptions. We take a maximum real time interval of 30 minutes around each detected interruption, obtaining a set of 26988 time series subsequences. Then, we compute the median of all these subsequences as a generic local representation (Figure \ref{fig:all_ints}). We also plot with dashed lines the median values of edits and selections per minute in the sessions with interruptions in order to give more context to the observed values.
%where another interruption  should not have been found. 
Below we describe some observations:
\begin{itemize}
\item \textit{In the center,} we find the interruption point. There is clearly a negative effect on the time series, as the area before and after the interruption is the area with the lowest activity. The activity is well below the median activity of time series with interruptions, showing that the effect is indeed more pronounced near interruptions.

@@

>>>>

\subsection{Local Analysis}

Having presented the global effect of the interruptions over the user productivity, we now focus on the local activity before and after interruptions. We take a maximum real time interval of 30 minutes around each detected interruption, obtaining a set of 26988 time series subsequences. Then, we compute the median of all these subsequences as a generic local representation (Figure \ref{fig:all_ints}). We also plot with dashed lines the median values of edits and selections per minute in the sessions with interruptions in order to give more context to the observed values.
%where another interruption  should not have been found. 
Below we describe some observations:
\begin{itemize}
\item \textit{In the center,} we find the interruption point. There is clearly a negative effect on the time series, as the area before and after the interruption is the area with the lowest activity. The activity is well below the median activity of time series with interruptions, showing that the effect is indeed more pronounced near interruptions.

@@

\section{Usage Data Collector}

\subsection{Data description}
The Usage Data Collector dataset is a big compendium of information about interaction data from users of Eclipse through December 2008 to August 2010 with the intention to keep record of how programmers are using the IDE. It's a framework that listens to the events triggered by the user and system like edition and navigation commands, the startup of a plug in or the closing of the platform. More specifically, UDC collects information about loaded bundles, commands accessed via keyboard shortcuts, actions invoked via menu or tool-bars, perspective changes, view usage and editor usage. It is a big dataset that contains information of around 1,800,000 users and has a total of 2,323,233,101 unique rows with 5 attributes each. The next table show a description of the attributes.

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Attributes in UDC data~\cite{KM06}. }
\label{tbl:kind_event}
\centering
\begin{tabular}{|p{1.7cm}|p{3.5cm}|} 
  \hline 
attribute & description \\  
  \hline 
    \hline 
userId &  Unique number that identifies a user \\
what & The action of the event (deactivated, activated, opened, executed, etc.)  \\
kind & What kind of event was executed (workbench, view, command, etc.)  \\
bundleId & Description of the event's package  \\
bundleVersion & Version of the bundle's event  \\
description & Description of the event\\
datetime & Date and time in UNIX format\\
  \hline
\end{tabular}
